---
title: "HW-3"
author: "Hector He"
date: "4/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
titanic <- read.csv('~/Desktop/Spring 2022/PSTAT 131/homework/homework-3/data/titanic.csv')
```

```{r}
library(tidyverse)
library(tidymodels)
library(naivebayes)
library(readr)
library(discrim)
library(magrittr)
library(corrr)
library(dplyr)
library(klaR)
```


```{r}
titanic <- titanic %>%
  mutate(survived = factor(survived, levels = c('Yes','No'))) %>%
  mutate(pclass = factor(pclass, levels = c('1','2','3')))
head(titanic)
```
```{r}
set.seed(2000)
titanic_split <- initial_split(titanic, prop = 0.5, strata = survived)
titanic_test <- testing(titanic_split)
titanic_train <- training(titanic_split)
```
we stratify on 'survived' hoping that we can get equal proportion of observations from both survivers and victims
```{r}
head(is.na.data.frame(titanic_train), n = 12)
```
age and cabin number are missing for some passengers
```{r}
titanic_train %>% 
  ggplot(aes(x = survived)) + geom_bar()
```
in the training set about 60 percent of passengers did not survive, and 30 percent survived, this should be consistent with the proportion in the entire dataset

```{r}
cor_titanic <- titanic_train %>%
  dplyr::select(passenger_id, age, sib_sp, parch, fare) %>%
  correlate()
rplot(cor_titanic)
```
strongly positively related: number of parents/children aboard vs number of spouses/siblings aboard
weakly positively related: number of parch/sib_sp vs fare
some people tend to bring their entire family aboard, the more family members, the higher the fare
strongly negatively related: number of spouses/siblings aboard vs age
weakly negatively related: number of parents/children aboard vs age
older people do not tend to bring their spouses/siblings/parents/children aboard
passenger_id is not related to anything, which makes sense since it is purely random

```{r}
titanic_recipe <- recipe(survived ~ pclass +sex +age +sib_sp +parch +fare, data = titanic_train) %>% 
  step_impute_linear(age, impute_with = imp_vars(pclass, fare)) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ age:fare) %>% 
  step_interact(terms = ~ starts_with('sex'):fare) %>% 
  step_center(all_predictors()) %>% 
  step_scale(all_predictors()) 
```

```{r}
glm_titanic_train <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")
glm_wkflow <- workflow() %>% 
  add_model(glm_titanic_train) %>% 
  add_recipe(titanic_recipe)
glm_fit <- fit(glm_wkflow, titanic_train)
glm_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()
```
```{r}
titanic_pre_glm <- predict(glm_fit, new_data = titanic_train, type = "prob")
titanic_pre_glm <- bind_cols(titanic_pre_glm, titanic_train)
head(titanic_pre_glm)
```
```{r}
augment(glm_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class) 
```
```{r}
glm_acc <- augment(glm_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
glm_acc
```
```{r}
lda_titanic_train <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")
lda_wkflow <- workflow() %>% 
  add_model(lda_titanic_train) %>% 
  add_recipe(titanic_recipe)
lda_fit <- fit(lda_wkflow, titanic_train)
lda_fit %>% 
  extract_fit_parsnip()
```
```{r}
titanic_pre_lda <- predict(lda_fit, new_data = titanic_train, type = "prob")
titanic_pre_lda <- bind_cols(titanic_pre_lda, titanic_train)
head(titanic_pre_lda)
```
```{r}
lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
lda_acc
```
```{r}
augment(lda_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class) 
```

```{r}
qda_titanic_train <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")
qda_wkflow <- workflow() %>% 
  add_model(qda_titanic_train) %>% 
  add_recipe(titanic_recipe)
qda_fit <- fit(qda_wkflow, titanic_train)
qda_fit %>% 
  extract_fit_parsnip()
```

```{r}
titanic_pre_qda <- predict(qda_fit, new_data = titanic_train, type = "prob")
titanic_pre_qda <- bind_cols(titanic_pre_qda, titanic_train)
head(titanic_pre_qda, n = 7)
```

```{r}
qda_acc <- augment(glm_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc
```

```{r}
nbayes_titanic_train <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 
nbayes_wkflow <- workflow() %>% 
  add_model(nbayes_titanic_train) %>% 
  add_recipe(titanic_recipe)
nbayes_fit <- fit(nbayes_wkflow, titanic_train)
nbayes_fit %>% 
  extract_fit_parsnip()
```

```{r}
library(e1071)
nbayes_fit <- naiveBayes(survived ~ pclass +sex +age +sib_sp +parch +fare, data = titanic_train)
nbayes_fit
```

```{r}
titanic_pre_nbayes <- predict(nbayes_fit, new_data = titanic_train, type = "prob")
titanic_pre_nbayes <- bind_cols(titanic_pre_nbayes, titanic_train)
head(titanic_pre_nbayes)
```

```{r}
pre_accuracies <- c(glm_acc$.estimate, lda_acc$.estimate, qda_acc$.estimate)
pre_models <- c("Logistic Regression", "LDA", "QDA")
pre_results <- tibble(accuracies = pre_accuracies, models = pre_models)
pre_results %>% 
  arrange(-accuracies)
```

```{r}
predict(qda_fit, new_data = titanic_test, type = "prob")
```

```{r}
augment(qda_fit, new_data = titanic_test) %>%
  conf_mat(truth = survived, estimate = .pred_class) 
```
```{r}
multi_metric <- metric_set(accuracy, sensitivity, specificity)
augment(qda_fit, new_data = titanic_test) %>%
  multi_metric(truth = survived, estimate = .pred_class)
```
```{r}
augment(qda_fit, new_data = titanic_test) %>%
  roc_curve(survived, .pred_No) %>%
  autoplot()
```
```{r}
qda_acc_test <- augment(qda_fit, new_data = titanic_test) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc_test
```
only 76.7 % accuracy for the testing set compared with the 83.5 % accuracy in the training set











